---
title: "Peer assesment 1"
output: html_document
---

###Loading and preprocessing the data
```{r, echo=TRUE}
dat<-read.csv("activity.csv")
```

###What is mean total number of steps taken per day?
```{r, echo=TRUE}
steps<-tapply(dat$steps,dat$date,sum,na.rm=TRUE)
hist(steps,xlab="steps",main="number of steps per day",col="light blue")
```

Mean number of steps taken per day
```{r, echo=TRUE}
mean(steps)
```

Median number of steps taken per day
```{r, echo=TRUE}
median(steps)
```

###What is the average daily activity pattern?
```{r, echo=TRUE}
interval <- tapply(dat$steps, dat$interval, mean, na.rm = TRUE)
plot(interval,main="average daily activity pattern",xlab="5-minute interval",ylab="average number of steps taken",type="l")
```

###Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
which(interval==max(interval), arr.ind=TRUE)
```
Time interval with maximun number of steps is 835


###Imputing missing values
Calculate and report the total number of missing values in the dataset 
```{r, echo=TRUE}
nrow(dat)-nrow(na.omit(dat))
```

Fill all of the missing values in the dataset with the mean
```{r, echo=TRUE}
mean_steps <- aggregate(steps ~ interval, data = dat, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(dat)) {
    obs <- dat[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(mean_steps, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fillNA <- c(fillNA, steps)
}

new_data <- dat
new_data$steps <- fillNA
new_steps <- aggregate(steps ~ date, data = new_data, sum, na.rm = TRUE)
hist(new_steps$steps, main = "Total steps by day", xlab = "day", col = "red")
```

Mean number of steps with no NA taken per day
```{r, echo=TRUE}
mean(new_steps$steps)
```

Median number of steps with no NA taken per day
```{r, echo=TRUE}
median(new_steps$steps)
```
Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

Values now are almost de same

###Are there differences in activity patterns between weekdays and weekends?
```{r,echo=TRUE}
library(lattice)
day <- weekdays(as.Date(dat$date))
daylevel <- vector()
for (i in 1:nrow(dat)) {
    if (day[i] == "Saturday") {
        daylevel[i] <- "Weekend"
    } else if (day[i] == "Sunday") {
        daylevel[i] <- "Weekend"
    } else {
        daylevel[i] <- "Weekday"
    }
}
dat$daylevel <- daylevel
dat$daylevel <- factor(dat$daylevel)

stepsByDay <- aggregate(steps ~ interval + daylevel, data = dat, mean)
names(stepsByDay) <- c("interval", "daylevel", "steps")
xyplot(steps ~ interval | daylevel, stepsByDay, type = "l", layout = c(1, 2), xlab = "Interval", 
       ylab ="Number of steps")
```

